Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Our approach expands on \cite{adv_upd}, who identified the collapse of
Q-learning for small time steps and suggested as a solution the Advantage Updating
algorithm with proper $\deltat$ scalings for the $V$ part and the
advantage part; testing was only
done on a quadratic-linear problem. Using a different normalization step
for $A$ (which forgoes the need to learn the normalization itself, thanks
to the parameterization \eqref{eq:Aparam}), we test Advantage Updating
for the first time on a variety on RL environments using deep networks,
establishing Deep Advantage Updating as a viable algorithm in this
setting.  Additionally, we provide formal proofs for the collapse of
Q-learning when $\deltat\to 0$, and for the non-collapse of Advantage
Updating, in a general setting.

>>>>

Our approach builds on \cite{adv_upd}, who identified the collapse of
Q-learning for small time steps and suggested as a solution the Advantage
Updating algorithm with proper $\deltat$ scalings for the $V$ part and
the advantage part; testing was only done on a quadratic-linear problem.
We expand on \cite{adv_upd} in several directions. First, we modify the
algorithm by
using a different normalization step for $A$, which forgoes the need to
learn the normalization itself, thanks to the parameterization
\eqref{eq:Aparam}. Second, we test Advantage Updating for the first time on a
variety on RL environments using deep networks, establishing Deep
Advantage Updating as a viable algorithm in this setting.  Third,
we provide formal proofs in a general setting for the collapse of Q-learning when $\deltat\to
0$, and for the non-collapse of Advantage Updating.
Fourth, we also discuss how to obtain $\deltat$-invariant exploration. Fifth, we
provide stringent experimental tests of the actual robustness to changing
$\deltat$.
